Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-09-30 prop_letter.tex
prop_letter.tex \section{Gleason} Global replace 	\iota_{*}\circ\mu_{*}^{\mathrm{B}} by 	\left[\mu_{*}^{\mathrm{B}}\right]_{*} .

@@

The first step toward a finite precision Born rule is to find a way
of replacing the computed probability by an interval. This can be
done by carefully picking a set of intervals and a rule to select
the correct interval when intervals are overlapping. For example,
consider the following collection of overlapping intervals: 
\begin{equation}
\begin{aligned}\mathscr{I}_{n}= & \set{\left[\tfrac{k-1}{2n},\tfrac{k+1}{2n}\right]\cap\left[0,1\right]}{k=0,\ldots,2n}\\
 & \cup\{\imposs,\necess\}
\end{aligned}
\end{equation}
which are overlapping intervals with length~$1/n$ except for the
intervals with length~$\left(2n\right)^{-1}$ at each end. As shown
in Table~\ref{tab:I_n}, we select the correct interval from these
overlapping intervals~$[\ell,r]$, and define $\textrm{Int}\left([\ell,r]\right)$,
the non-overlapping interior part of an interval.
\begin{table}
\caption{\label{tab:I_n}Intervals in $\mathscr{I}_{n}$, their lengths, and
their interiors, where $2\mid k$ means $k$ is even, and $2\nmid k$
means $k$ is odd. Although intervals~$[\ell,r]$ are overlapping,
their interior~$\textrm{Int}\left([\ell,r]\right)$ are non-overlapping.
See Table~\ref{tab:I_2} for a concrete example when $n=2$.}

\begin{tabular}{cccc}
\toprule 
\addlinespace
$k$ & $[\ell,r]$ & $r-\ell$ & $\textrm{Int}\left([\ell,r]\right)$\tabularnewline\addlinespace
\midrule
\midrule 
\addlinespace
 & $\imposs$ & $0$ & $\imposs$\tabularnewline\addlinespace
\midrule 
\addlinespace
$0$ & $\left[0,\tfrac{1}{2n}\right]$ & $\tfrac{1}{2n}$ & $\left(0,\tfrac{0.5}{2n}\right]$\tabularnewline\addlinespace
\midrule 
\addlinespace
\begin{tabular}{c}
$0<k<2n$\tabularnewline
and $2\nmid k$\tabularnewline
\end{tabular} & $\left[\tfrac{k-1}{2n},\tfrac{k+1}{2n}\right]$ & $\tfrac{1}{n}$ & $\left(\tfrac{k-0.5}{2n},\tfrac{k+0.5}{2n}\right)$\tabularnewline\addlinespace
\midrule 
\addlinespace
\begin{tabular}{c}
$0<k<2n$\tabularnewline
and $2\mid k$\tabularnewline
\end{tabular} & \multirow{1}{*}{$\left[\tfrac{k-1}{2n},\tfrac{k+1}{2n}\right]$} & $\tfrac{1}{n}$ & $\left[\tfrac{k-0.5}{2n},\tfrac{k+0.5}{2n}\right]$\tabularnewline\addlinespace
\midrule 
\addlinespace
$2n$ & $\left[\tfrac{2n-1}{2n},1\right]$ & $\tfrac{1}{2n}$ & $\left[\tfrac{2n-0.5}{2n},1\right)$\tabularnewline\addlinespace
\midrule 
\addlinespace
 & $\necess$ & $0$ & $\necess$\tabularnewline\addlinespace
\bottomrule
\end{tabular}
\end{table}
 Table~\ref{tab:I_2} lists a special case $\mathscr{I}_{2}$ to
illustrate these intervals and their interior parts more clearly.
\begin{table}
\caption{\label{tab:I_2}Intervals in $\mathscr{I}_{2}$, , their lengths,
and their interiors. Although intervals~$[\ell,r]$ are overlapping,
their interior~$\textrm{Int}\left([\ell,r]\right)$ are non-overlapping.}

\begin{tabular}{cccc}
\toprule 
\addlinespace
$k$ & $[\ell,r]$ & $r-\ell$ & $\textrm{Int}\left([\ell,r]\right)$\tabularnewline\addlinespace
\midrule
\midrule 
\addlinespace
 & $\imposs$ & $0$ & $\imposs$\tabularnewline\addlinespace
\midrule 
\addlinespace
$0$ & $\left[0,\tfrac{1}{4}\right]$ & $\tfrac{1}{4}$ & $\left(0,\tfrac{1}{8}\right]$\tabularnewline\addlinespace
\midrule 
\addlinespace
$1$ & $\left[0,{\textstyle \tfrac{1}{2}}\right]$ & $\tfrac{1}{2}$ & $\left(\tfrac{1}{8},\tfrac{3}{8}\right)$\tabularnewline\addlinespace
\midrule 
\addlinespace
$2$ & $\left[\tfrac{1}{4},\tfrac{3}{4}\right]$ & $\tfrac{1}{2}$ & $\left[\tfrac{3}{8},\tfrac{5}{8}\right]$\tabularnewline\addlinespace
\midrule 
\addlinespace
$3$ & $\left[\tfrac{1}{2},1\right]$ & $\tfrac{1}{2}$ & $\left(\tfrac{5}{8},\tfrac{7}{8}\right)$\tabularnewline\addlinespace
\midrule 
\addlinespace
$4$ & $\left[\tfrac{1}{4},1\right]$ & $\tfrac{1}{4}$ & $\left[\tfrac{7}{8},1\right)$\tabularnewline\addlinespace
\midrule 
\addlinespace
 & $\necess$ & $0$ & $\necess$\tabularnewline\addlinespace
\bottomrule
\end{tabular}
\end{table}
 Then, given a real-valued probability~$x$, we will select the interval~$\iota_{n}\left(x\right)=[\ell,r]$
if $x\in\textrm{Int}\left([\ell,r]\right)$.

\begin{thm}[Finite-precision Extension of the Born rule]\label{thm:Finite-precision-Born}For
any state $\rho$ on a three-dimensional Hilbert space, $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$
is a QIVPM, where $\circ$ is the function concatenation.\end{thm}

\noindent Since $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$ clearly satisfies
Eqs.~(\ref{eq:QIVPM-constraints}), the condition that needs to be
checked is Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}).
Given $x_{0}$, $x_{1}$, and $x_{0}+x_{1}\in\left[0,1\right]$, it
is easy to verify that
\begin{equation}
\iota_{n}\left(x_{0}+x_{1}\right)\subseteq\iota_{n}\left(x_{0}\right)+\iota_{n}\left(x_{1}\right)\,.\label{eq:iota-add}
\end{equation}
This implies Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
when $P_{0}$ and $P_{1}$ are orthogonal. When $P_{0}$ and $P_{1}$
are not orthogonal on a three-dimensional Hilbert space, we have two
possibilities:
\begin{itemize}
\item Their complements are orthogonal so that we can apply Eq.~(\ref{eq:iota-add})
on their complements.
\item One of them projects onto a subspace of what the other one projects
onto.
\end{itemize}
\noindent No matter which case holds, Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
can be deduced easily. Therefore, $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$
is indeed a QIVPM.

As a concrete example of Thm.~\ref{thm:Finite-precision-Born}, when
$n=2$, two states~$\rho_{0}=\frac{1}{3}\cdot\proj{0}+\frac{1}{3}\cdot\proj{1}+\frac{1}{3}\cdot\proj{2}$
and $\rho_{1}=\frac{7}{24}\cdot\proj{0}+\frac{1}{3}\cdot\proj{1}+\frac{3}{8}\cdot\proj{2}$
can induce two QIVPMs~$\iota_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}}$
and $\iota_{2}\circ\mu_{\rho_{1}}^{\mathrm{B}}$. Given any projector
$P$ in the minimal subspace of events containing $\proj{0}$, $\proj{1}$,
and $\proj{2}$, $\events_{C}$, the interval-valued probability of
the induced QIVPMs, $\iota_{2}\left(\mu_{\rho_{0}}^{\mathrm{B}}\left(P\right)\right)$
and $\iota_{2}\left(\mu_{\rho_{1}}^{\mathrm{B}}\left(P\right)\right)$,
can be computed straightforwardly in Table~\ref{tab:Compute-the-QIVPM}.
\begin{table}
\caption{\label{tab:Compute-the-QIVPM}Compute $\iota_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}}$
and $\iota_{2}\circ\mu_{\rho_{1}}^{\mathrm{B}}$ based on $\mu_{\rho_{0}}^{\mathrm{B}}$
and $\mu_{\rho_{1}}^{\mathrm{B}}$ on $\events_{C}$.}

@@

@@

Our framework allows us to generalize the above theorem to Born QIVPMs~$\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$:
The collection of states consistent $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$
gets closer and closer to $\rho$ as the intervals get narrower and
narrower, eventually collapsing to $\rho$ when the intervals become
infinitely precise real numbers covering the real line. To state this
result, we need to introduce a notion of distance between two states~$\rho$
and $\rho'$ as $\left\Vert \rho-\rho'\right\Vert =\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{\rho-\rho'}{\psi}\right|$~\citep{544199}.
By replacing the QIVPM~$\bar{\mu}$ in Thm.~\ref{cor:Gleason's}
by a Born QIVPM~$\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$, we obtain
the following theorem that estimates the states consistent with $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$.

\begin{thm}[Finite-precision Extension of Gleason's theorem for the
Born QIVPMs]\label{thm:Finite-precision-Gleason}In a Hilbert space
$\Hilb$ of dimension $3$, given any state~$\rho$, if a state~$\rho'\in\coreBorn\left(\iota_{n}\circ\mu_{\rho}^{\mathrm{B}},\events\right)$,
then their distance~$\left\Vert \rho-\rho'\right\Vert \le\frac{1}{n}$.\end{thm}

\noindent If a state~$\rho'$ is consistent with $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$,
the difference between their Born quantum probabilities on any 1-dimensioal
projector~$\proj{\psi}$, $\left|\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)-\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)\right|$,
must be bounded by $1/n$ which implies $\left\Vert \rho-\rho'\right\Vert \le\frac{1}{n}$
by definition. For example, Table~\ref{tab:Compute-the-QIVPM} shows
that $\rho_{0}$ is consistent with $\iota_{2}\circ\mu_{\rho_{1}}^{\mathrm{B}}$
and $\rho_{1}$ is consistent with $\iota_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}}$
both on every projectors in $\events_{C}$. Indeed, they are consistent
with each other on every projectors in $\events$ that implies $\left\Vert \rho_{0}-\rho_{1}\right\Vert \le\frac{1}{2}$
by Thm.~\ref{thm:Finite-precision-Gleason}. This is true because
the exact value of $\left\Vert \rho_{0}-\rho_{1}\right\Vert $ is
$\frac{1}{24}$~\citep{544199}.

If a QIVPM is not \emph{a priori} known to be induced by a state,
there are some QIVPMs that cannot be consistent with any state.

\begin{tabular}{cc}
\toprule 
\addlinespace
$P$ & $\bar{\mu}\left(P\right)$\tabularnewline\addlinespace
\midrule
\midrule 
\addlinespace
$\mathbb{0}$, $\proj{0}$, $\proj{\ps}$, and $\proj{\ps'}$ & $\imposs$\tabularnewline\addlinespace
\midrule 
\addlinespace
$\mathbb{1}$, $\mathbb{1}-\proj{0}$, $\mathbb{1}-\proj{\ps}$, and
$\mathbb{1}-\proj{\ps'}$ & $\necess$\tabularnewline\addlinespace
\midrule 
\addlinespace
All other projectors & $\unknown$\tabularnewline\addlinespace
\bottomrule
\end{tabular}
\end{table}
Next we will prove $\coreBorn\left(\bar{\mu},\events\right)$ is an
empty set by contradiction. Suppose there is a state $\rho=\sum_{j=1}^{N}q_{j}\proj{\phi_{j}}\in\coreBorn\left(\bar{\mu},\events\right)$,
where $\sum_{j=1}^{N}q_{j}=1$ and $q_{j}>0$. Since $\mu_{\rho}^{\mathrm{B}}(P)\in\bar{\mu}(P)$
for any~$P$, the state~$\rho$ must satisfy: 
\begin{equation}
\mu_{\rho}^{\mathrm{B}}(\proj{0})=\mu_{\rho}^{\mathrm{B}}(\proj{\ps})=\mu_{\rho}^{\mathrm{B}}(\proj{\ps'})=0\,,
\end{equation}
which implies $\ip{\phi_{j}}{0}=\ip{\phi_{j}}{\ps}=\ip{\phi_{j}}{\ps'}=0$
for all $j$. The last equation never holds proving the theorem. Thus,
there is no state consistent with the QIVPM on all projectors~$P\in\events$,
so Gleason's theorem cannot be extended to general QIVPMs.

>>>>

In Sec.~\ref{sec:Interval-Uncertainty}, we discussed how states
consistent with a QIVPM~$\bar{\mu}$ on the projectors in a subspace
of event~$\events'$. In particular, if $\events'$ commutes, $\bar{\mu}$
restricting on $\events'$ is essentially a classical IVPM, and Thm.~\ref{thm:Shapley}
claims that there is always a state~$\rho$ consistent with $\bar{\mu}$.
In this section, we want to shift our attention to consider states
consistent with $\bar{\mu}$ on every event, $\coreBorn\left(\bar{\mu},\events\right)$,
so that these states could characterize $\bar{\mu}$ comprehensively.
When the intervals are infinitely precise, i.e., $\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$,
QIVPMs become to quantum probability measures~\citep{HOSTunpublished},
and Gleason's theorem claims that there is always a unique state consistent
with $\bar{\mu}:\events\rightarrow\mathscr{I}_{\infty}$~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}.
However, if we consider general QIVPMs mapping to an \emph{arbitrary}
set of intervals, there is a QIVPM that no state can be consistent
with it.

\begin{tabular}{cc}
\toprule 
\addlinespace
$P$ & $\bar{\mu}\left(P\right)$\tabularnewline\addlinespace
\midrule
\midrule 
\addlinespace
$\mathbb{0}$, $\proj{0}$, $\proj{\ps}$, and $\proj{\ps'}$ & $\imposs$\tabularnewline\addlinespace
\midrule 
\addlinespace
$\mathbb{1}$, $\mathbb{1}-\proj{0}$, $\mathbb{1}-\proj{\ps}$, and
$\mathbb{1}-\proj{\ps'}$ & $\necess$\tabularnewline\addlinespace
\midrule 
\addlinespace
All other projectors & $\unknown$\tabularnewline\addlinespace
\bottomrule
\end{tabular}
\end{table}
Next we will prove $\coreBorn\left(\bar{\mu},\events\right)$ is an
empty set by contradiction. Suppose there is a state $\rho=\sum_{j=1}^{N}q_{j}\proj{\phi_{j}}\in\coreBorn\left(\bar{\mu},\events\right)$,
where $\sum_{j=1}^{N}q_{j}=1$ and $q_{j}>0$. Since $\mu_{\rho}^{\mathrm{B}}(P)\in\bar{\mu}(P)$
for any~$P$, the state~$\rho$ must satisfy: 
\begin{equation}
\mu_{\rho}^{\mathrm{B}}(\proj{0})=\mu_{\rho}^{\mathrm{B}}(\proj{\ps})=\mu_{\rho}^{\mathrm{B}}(\proj{\ps'})=0\,,
\end{equation}
which implies $\ip{\phi_{j}}{0}=\ip{\phi_{j}}{\ps}=\ip{\phi_{j}}{\ps'}=0$
for all $j$. The last equation never holds proving the theorem.

In other words, if the measurement intervals are too imprecise, the
results we get might contradict to each other, and exclude all possible
states consistent with the measurement results. There are many ways
to avoid these kind of too imprecise intervals~\citep{HOSTunpublished}.
Following, we consider a concrete family of intervals and QIVPMs~$\bar{\mu}$
such that if we monotonically shrink the length of intervals, the
states consistent with $\bar{\mu}$ will be closer and closer to $\rho$
which inducing $\bar{\mu}$.
\begin{equation}
\begin{aligned}\mathscr{I}_{n}= & \set{\left[\tfrac{k-1}{2n},\tfrac{k+1}{2n}\right]\cap\left[0,1\right]}{k=0,\ldots,2n}\\
 & \cup\{\imposs,\necess\}
\end{aligned}
\end{equation}
which are overlapping intervals with length~$1/n$ except for the
intervals with length~$\left(2n\right)^{-1}$ at each end. As shown
in Table~\ref{tab:I_n}, we select the correct interval from these
overlapping intervals~$[\ell,r]$, and define $\textrm{Int}\left([\ell,r]\right)$,
the non-overlapping interior part of an interval.
\begin{table}
\caption{\label{tab:I_n}Intervals in $\mathscr{I}_{n}$, their lengths, and
their interiors, where $2\mid k$ means $k$ is even, and $2\nmid k$
means $k$ is odd. Although intervals~$[\ell,r]$ are overlapping,
their interior~$\textrm{Int}\left([\ell,r]\right)$ are non-overlapping.
See Table~\ref{tab:I_2} for a concrete example when $n=2$.}

\begin{tabular}{cccc}
\toprule 
\addlinespace
$k$ & $[\ell,r]$ & $r-\ell$ & $\textrm{Int}\left([\ell,r]\right)$\tabularnewline\addlinespace
\midrule
\midrule 
\addlinespace
 & $\imposs$ & $0$ & $\imposs$\tabularnewline\addlinespace
\midrule 
\addlinespace
$0$ & $\left[0,\tfrac{1}{2n}\right]$ & $\tfrac{1}{2n}$ & $\left(0,\tfrac{0.5}{2n}\right]$\tabularnewline\addlinespace
\midrule 
\addlinespace
\begin{tabular}{c}
$0<k<2n$\tabularnewline
and $2\nmid k$\tabularnewline
\end{tabular} & $\left[\tfrac{k-1}{2n},\tfrac{k+1}{2n}\right]$ & $\tfrac{1}{n}$ & $\left(\tfrac{k-0.5}{2n},\tfrac{k+0.5}{2n}\right)$\tabularnewline\addlinespace
\midrule 
\addlinespace
\begin{tabular}{c}
$0<k<2n$\tabularnewline
and $2\mid k$\tabularnewline
\end{tabular} & \multirow{1}{*}{$\left[\tfrac{k-1}{2n},\tfrac{k+1}{2n}\right]$} & $\tfrac{1}{n}$ & $\left[\tfrac{k-0.5}{2n},\tfrac{k+0.5}{2n}\right]$\tabularnewline\addlinespace
\midrule 
\addlinespace
$2n$ & $\left[\tfrac{2n-1}{2n},1\right]$ & $\tfrac{1}{2n}$ & $\left[\tfrac{2n-0.5}{2n},1\right)$\tabularnewline\addlinespace
\midrule 
\addlinespace
 & $\necess$ & $0$ & $\necess$\tabularnewline\addlinespace
\bottomrule
\end{tabular}
\end{table}
Then, given a real-valued probability~$x$, we will select the interval~$\iota_{n}\left(x\right)=[\ell,r]$
if $x\in\textrm{Int}\left([\ell,r]\right)$.

\begin{thm}[Finite-precision Extension of the Born rule]\label{thm:Finite-precision-Born}For
any state $\rho$ on a three-dimensional Hilbert space, a function~$\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}:\events\rightarrow\mathscr{I}_{n}$
defined by $\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}\left(P\right)=\iota_{n}\left(\mu_{\rho}^{\mathrm{B}}\left(P\right)\right)$
is a QIVPM.\end{thm}

\noindent Since $\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$ clearly
satisfies Eqs.~(\ref{eq:QIVPM-constraints}), the condition that
needs to be checked is Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}).
Given $x_{0}$, $x_{1}$, and $x_{0}+x_{1}\in\left[0,1\right]$, it
is easy to verify that
\begin{equation}
\iota_{n}\left(x_{0}+x_{1}\right)\subseteq\iota_{n}\left(x_{0}\right)+\iota_{n}\left(x_{1}\right)\,.\label{eq:iota-add}
\end{equation}
This implies Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
when $P_{0}$ and $P_{1}$ are orthogonal. When $P_{0}$ and $P_{1}$
are not orthogonal on a three-dimensional Hilbert space, we have two
possibilities:
\begin{itemize}
\item Their complements are orthogonal so that we can apply Eq.~(\ref{eq:iota-add})
on their complements.
\item One of them projects onto a subspace of what the other one projects
onto.
\end{itemize}
\noindent No matter which case holds, Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
can be deduced easily. Therefore, $\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$
is indeed a QIVPM.

\yutsung{Clean up until here.}

@@

If a QIVPM is not \emph{a priori} known to be induced by a state,

\noindent Thus, there is no state consistent with the QIVPM on all
projectors~$P\in\events$, so Gleason's theorem cannot be extended
to general QIVPMs.

The first step toward a finite precision Born rule is to find a way
of replacing the computed probability by an interval. This can be
done by carefully picking a set of intervals and a rule to select
the correct interval when intervals are overlapping. For example,
consider the following collection of overlapping intervals:

Table~\ref{tab:I_2} lists a special case $\mathscr{I}_{2}$ to illustrate
these intervals and their interior parts more clearly.
\begin{table}
\caption{\label{tab:I_2}Intervals in $\mathscr{I}_{2}$, , their lengths,
and their interiors. Although intervals~$[\ell,r]$ are overlapping,
their interior~$\textrm{Int}\left([\ell,r]\right)$ are non-overlapping.}

\begin{tabular}{cccc}
\toprule 
\addlinespace
$k$ & $[\ell,r]$ & $r-\ell$ & $\textrm{Int}\left([\ell,r]\right)$\tabularnewline\addlinespace
\midrule
\midrule 
\addlinespace
 & $\imposs$ & $0$ & $\imposs$\tabularnewline\addlinespace
\midrule 
\addlinespace
$0$ & $\left[0,\tfrac{1}{4}\right]$ & $\tfrac{1}{4}$ & $\left(0,\tfrac{1}{8}\right]$\tabularnewline\addlinespace
\midrule 
\addlinespace
$1$ & $\left[0,{\textstyle \tfrac{1}{2}}\right]$ & $\tfrac{1}{2}$ & $\left(\tfrac{1}{8},\tfrac{3}{8}\right)$\tabularnewline\addlinespace
\midrule 
\addlinespace
$2$ & $\left[\tfrac{1}{4},\tfrac{3}{4}\right]$ & $\tfrac{1}{2}$ & $\left[\tfrac{3}{8},\tfrac{5}{8}\right]$\tabularnewline\addlinespace
\midrule 
\addlinespace
$3$ & $\left[\tfrac{1}{2},1\right]$ & $\tfrac{1}{2}$ & $\left(\tfrac{5}{8},\tfrac{7}{8}\right)$\tabularnewline\addlinespace
\midrule 
\addlinespace
$4$ & $\left[\tfrac{1}{4},1\right]$ & $\tfrac{1}{4}$ & $\left[\tfrac{7}{8},1\right)$\tabularnewline\addlinespace
\midrule 
\addlinespace
 & $\necess$ & $0$ & $\necess$\tabularnewline\addlinespace
\bottomrule
\end{tabular}
\end{table}

As a concrete example of Thm.~\ref{thm:Finite-precision-Born}, when
$n=2$, two states~$\rho_{0}=\frac{1}{3}\cdot\proj{0}+\frac{1}{3}\cdot\proj{1}+\frac{1}{3}\cdot\proj{2}$
and $\rho_{1}=\frac{7}{24}\cdot\proj{0}+\frac{1}{3}\cdot\proj{1}+\frac{3}{8}\cdot\proj{2}$
can induce two QIVPMs~$\left[\mu_{\rho_{0}}^{\mathrm{B}}\right]_{2}$
and $\left[\mu_{\rho_{1}}^{\mathrm{B}}\right]_{2}$. Given any projector
$P$ in the minimal subspace of events containing $\proj{0}$, $\proj{1}$,
and $\proj{2}$, $\events_{C}$, the interval-valued probability of
the induced QIVPMs, $\iota_{2}\left(\mu_{\rho_{0}}^{\mathrm{B}}\left(P\right)\right)$
and $\iota_{2}\left(\mu_{\rho_{1}}^{\mathrm{B}}\left(P\right)\right)$,
can be computed straightforwardly in Table~\ref{tab:Compute-the-QIVPM}.
\begin{table}
\caption{\label{tab:Compute-the-QIVPM}Compute $\left[\mu_{\rho_{0}}^{\mathrm{B}}\right]_{2}$
and $\left[\mu_{\rho_{1}}^{\mathrm{B}}\right]_{2}$ based on $\mu_{\rho_{0}}^{\mathrm{B}}$
and $\mu_{\rho_{1}}^{\mathrm{B}}$ on $\events_{C}$.}

@@

Our framework allows us to generalize the above theorem to Born QIVPMs~$\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$:
The collection of states consistent $\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$
gets closer and closer to $\rho$ as the intervals get narrower and
narrower, eventually collapsing to $\rho$ when the intervals become
infinitely precise real numbers covering the real line. To state this
result, we need to introduce a notion of distance between two states~$\rho$
and $\rho'$ as $\left\Vert \rho-\rho'\right\Vert =\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{\rho-\rho'}{\psi}\right|$~\citep{544199}.
By replacing the QIVPM~$\bar{\mu}$ in Thm.~\ref{cor:Gleason's}
by a Born QIVPM~$\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$, we obtain
the following theorem that estimates the states consistent with $\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$.

\begin{thm}[Finite-precision Extension of Gleason's theorem for the
Born QIVPMs]\label{thm:Finite-precision-Gleason}In a Hilbert space
$\Hilb$ of dimension $3$, given any state~$\rho$, if a state~$\rho'\in\coreBorn\left(\left[\mu_{\rho}^{\mathrm{B}}\right]_{n},\events\right)$,
then their distance~$\left\Vert \rho-\rho'\right\Vert \le\frac{1}{n}$.\end{thm}

\yutsung{Compare the norm we used with other distances. For example,
the trace distance defined in Sec.~9.2.1 in Nielsen and Chuang~\citep{544199}.}

\noindent If a state~$\rho'$ is consistent with $\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$,
the difference between their Born quantum probabilities on any 1-dimensioal
projector~$\proj{\psi}$, $\left|\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)-\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)\right|$,
must be bounded by $1/n$ which implies $\left\Vert \rho-\rho'\right\Vert \le\frac{1}{n}$
by definition. For example, Table~\ref{tab:Compute-the-QIVPM} shows
that $\rho_{0}$ is consistent with $\left[\mu_{\rho_{1}}^{\mathrm{B}}\right]_{2}$
and $\rho_{1}$ is consistent with $\left[\mu_{\rho_{0}}^{\mathrm{B}}\right]_{2}$
both on every projectors in $\events_{C}$. Indeed, they are consistent
with each other on every projectors in $\events$ that implies $\left\Vert \rho_{0}-\rho_{1}\right\Vert \le\frac{1}{2}$
by Thm.~\ref{thm:Finite-precision-Gleason}. This is true because
the exact value of $\left\Vert \rho_{0}-\rho_{1}\right\Vert $ is
$\frac{1}{24}$~\citep{544199}.

@@
